Implementation of a stable, high-power optical lattice for quantum gas microscopy

### 2018-06-13 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
Abstract rewording

\date{\today}
\begin{abstract}
  We describe the design and implementation of a stable high-power \unit{1064}{nm} laser system for use in experiments with ultracold atoms trapped in optical lattices. The system is based on a low-noise laser amplified by an array of four heavily modified, high-power fiber amplifiers. The beam intensity is stabilized and controlled with a nonlinear feedback loop. Using real-time monitoring of the resulting optical lattice, we demonstrate a shot-to-shot stability of the lattice position at 1\% of the lattice spacing and a long-term (six month) stability of 0.5\% RMS of the lattice spacing itself.
\end{abstract}
\maketitle

>>>>

\date{\today}
\begin{abstract}
  We describe the design and implementation of a stable high-power \unit{1064}{nm} laser system to generate optical lattices for experiments with ultracold quantum gases. The system is based on a low-noise laser amplified by an array of four heavily modified, high-power fiber amplifiers. The beam intensity is stabilized and controlled with a nonlinear feedback loop. Using real-time monitoring of the resulting optical lattice, we demonstrate a shot-to-shot stability of the lattice position at 1\% of the lattice spacing and a long-term (six month) stability of 0.5\% RMS of the lattice spacing itself.
\end{abstract}
\maketitle
